A conditional permutation-based approach to test confounder and center effects in machine learning models

### 2021-10-22 simulated/normality_and_linearity_violation.tex

\hypertarget{an-example-of-model-non-linearity-in-the-presence-of-a-linear-predictor.}{%
\section{An example of model non-linearity in the presence of a linear
predictor.}\label{an-example-of-model-non-linearity-in-the-presence-of-a-linear-predictor.}}

Notebook available on-line:
https://github.com/spisakt/mlconfound\_manuscript/tree/main/simulated/normality\_and\_linearity\_violation.ipynb

@@

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_0.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_1.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_2.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_3.png}
\caption{png}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_5_1.png}
\caption{png}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_7_1.png}
\caption{png}
\end{figure}

>>>>

\hypertarget{an-example-of-model-non-linearity-in-the-presence-of-a-linear-predictor.}{%
\section{An example of model non-linearity in the presence of a linear
predictor.}\label{an-example-of-model-non-linearity-in-the-presence-of-a-linear-predictor.}}
\label{sup:nomlinviol}

Notebook available on-line:

https://github.com/spisakt/mlconfound\_manuscript/tree/main/simulated/normality\_and\_linearity\_violation.ipynb

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.15\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_0.png}
\includegraphics[width=0.15\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_1.png}
\includegraphics[width=0.15\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_2.png}
\includegraphics[width=0.15\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_3.png}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_5_1.png}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\paperwidth]{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_7_1.png}
\end{figure}
